Approximation as Differentiation

### 2025-04-01 notes.tex
Rename.
FdVect.

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{C}F$ and category of families $\Fam(C)$ (\secref{grothendieck})
\item Examples of useful categories with biproducts:
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FdVect_k$ of finite-dimensional vector spaces over a field $k$ (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

@@

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/set-indexed-product}
\input{notes/sec/grothendieck}
\input{notes/sec/galois}

>>>>

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{C}F$ and category of families $\Fam(C)$ (\secref{grothendieck})
\item Examples of useful categories with biproducts (\secref{categories-with-biproducts}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FdVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

@@

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/set-indexed-product}
\input{notes/sec/grothendieck}
\input{notes/sec/some-categories-with-biproducts}

### 2025-04-01 notes/sec/some-categories-with-biproducts.tex
FdVect.

>>>>

\begin{definition}[Vector space over a field $F$]
Suppose $F$ a field with addition of elements written $a + b$ and multiplication written $a \mult b$. Then a
\emph{vector space $V = (V, +, \mult)$ over $F$} (overloading $+$ and $\mult$) is a set $V$ equipped with
addition of vectors $+: V^2 \to V$ and scalar multiplication $\mult: F \times V \to V$ where $(V,+)$ is an
abelian group (with identity element $0_V$ and additive inverse $-v$ for any $v \in V$) and the vector
operations are compatible with the field operations in that the following equations hold:
\begin{itemize}
\item $1 \mult v = v$
\item $(a \mult b) \mult v = a \mult (b \mult v)$
\item $(a + b) \mult v = (a \mult v) + (b \mult v)$
\item $a \mult (u + v) = (a \mult u) + (b \mult v)$
\end{itemize}
\end{definition}

Up to isomorphism a finite-dimensional vector space over $F$ of dimension $n \in \Nat$ is $(F^n, +, \mult)$
with $+$ and $\mult$ defined component-wise. Define $\FdVect_F$ to be the category where
\begin{itemize}
\item the objects are natural numbers $n$ paired with an $n$-dimensional vector space $F^n$
\end{itemize}
